Large Language Models in Reinforcement Learning - A Comparison of Methods

### 2023-11-14 doc/paper.tex
do good things

Notably, both policy influencing and A2C2 receive much higher rewards than reward shaping and the baseline right from the first episode. This makes sense as the environment is so simple that the LLM seems not to have any problem giving sensible instructions to directly influence the policy most of the time. However, we notice from the graph that policy influencing alone consistently gives a significant dip in received reward after the first few episodes, which it later compensates for, following a similar trajectory to that of reward shaping after about 50 episodes. We believe this could be a sign of the policy influencing being somewhat overly influential in changing the logits early on, because the logits initially have low values. As the PPO learns the environment, the magnitude of the logits increases, which at some point leads to conflicting contributions to the logits from the LLM and from the PPO. As the dip stops and performance increases again, this is likely due to the PPO becoming more influencing than the LLM after having started to learn the environment properly. We also notice that this dip is completely removed with A2C2, which could signify that the added reward shaping helps the PPO learn faster, enabling it to increase the influence from PPO on the logits faster.

>>>>

Notably, both policy influencing and A2C2 receive much higher rewards than reward shaping and the baseline right from the first episode. This makes sense as the environment is so simple that the LLM seems not to have any problem giving sensible instructions to directly influence the policy most of the time. However, we notice from the graph that policy influencing alone consistently gives a significant dip in received reward after the first few episodes, which it later compensates for, following a similar trajectory to that of reward shaping after about 50 episodes. We believe this happens due to the magnitude of the logits increasing over time, meaning the LLM suggestions contribute less and the baseline PPO starts to overtake the majority of influence in actions being taken. Because the policy hasn't trained sufficiently yet, this makes the agent perform worse than when the LLM contributed more. We discuss this more in depth in the \nameref{sec:appendixtext}. We also notice that this dip is almost completely removed with A2C2, which might be because reward shaping leads to the policy network being better trained by the time the logits increase.
